HO unification from object language to meta language

### 2024-02-25 paper/main.tex
update main.tex

The compilation step is meant to recover the higher-order variables of the OL,
expressed in a first order way, by replacing them with higher-order variables in
the ML. In particular, every time a variable of the OL is encountered in the
original term, it is replaced with a meta variable, and if the OL variable is
applied to a list of distinct names $L$, then this list becomes the scope of the variable. 
For all the other constructors of
\elpiIn{tm}, the same term constructor is returned and its arguments are
recursively compiled. The predicate in charge for term compilation is:\\
\elpiIn{type comp tm -> tm -> links -> links -> subst -> subst -> o}.
Where, we take the term of the OL, produce the term of the ML, take a list
of link and produce a list of new links, take a substitution and return a 
new substitution.

>>>>

The compilation step is meant to recover the higher-order variables of the OL,
expressed in a first order way, by replacing them with higher-order variables in
the ML. In particular, every time a variable of the OL is encountered in the
original term, it is replaced with a meta variable, and if the OL variable is
applied to a list of distinct names $L$, then this list becomes the scope of the variable. 
For all the other constructors of
\elpiIn{tm}, the same term constructor is returned and its arguments are
recursively compiled. The predicate in charge for term compilation is:

\elpiIn{type comp tm -> tm -> links -> links -> subst -> subst -> o}.

\noindent
where, we take the term of the OL, produce the term of the ML, take a list
of link and produce a list of new links, take a substitution and return a 
new substitution.
